Gas-Efficient Parameter Verification for Blockchain Smart Contracts Using Off-Chain Validators

### 2024-10-10 papers/assertion-contract/fc2025/paper.tex
Update citations and related work section

\lstdefinelanguage{solidity}{
  backgroundcolor=\color{pink!20},
  keywords={contract, function, public, int},
  keywordstyle=\bfseries\color{blue},
  commentstyle=\itshape\color{green!40!black},
  basicstyle=\ttfamily,
  morecomment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]",
  sensitive=true
}
\begin{document}
%
\title{Gas-Efficient Parameter Verification for Blockchain Smart Contracts Using Off-Chain Validators}
%
\titlerunning{Off-Chain Parameter Verification Approach: Gas-Efficient}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and Peter Thiemann\orcidID{0000-0002-9000-1239}}
%
\authorrunning{Ha Doan, P. Thiemann}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Freiburg, Germany \\
  \email{\{doanha,thiemann\}@informatik.uni-freiburg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
In certain blockchain scenarios, verifying the properties of parameters may require significant gas costs or be infeasible due to gas limits. This study proposes a distributed verification protocol to address these challenges. The core concept involves offloading the verification process to validators, who attempt to find counterexamples or proofs off-chain. If a counterexample is discovered, it can be submitted for re-verification on-chain. If validated, the parameter is discarded; otherwise, the correctness of the parameter is guaranteed through a proof-of-work incentive mechanism, encouraging validators to participate in the distributed verification process. To implement these ideas, we propose a practical model that also tackles potential security concerns. We developed a prototype of the protocol and conducted a cost analysis, demonstrating its gas efficiency and practical utility.
\keywords{blockchain, off-chain verification, gas optimization, proof-of-work, distributed verification}
\end{abstract}
%
%
%
\section{Introduction}
\label{sec:introduction}
\lstset{language=solidity}
A smart contract is a critical component of blockchain technology, with applications ranging from simple tasks like auctions to more complex systems such as decentralized markets. However, broader adoption of smart contracts faces challenges, with gas costs being among the most significant. Every computation performed by a smart contract on the blockchain incurs a cost, as each unit of computation and storage consumed by an algorithm must be paid for due to the burden it places on the system \cite{eth-whitepaper,yellowpaper}.

@@

Another scenario involves interactions with external data sources. Since smart contracts cannot directly access off-chain data, blockchain oracles supply this information. When external data becomes available, an oracle invokes a smart contract with the relevant information.

@@

Smart contract languages like Solidity, Vyper, Michelson, and Plutus support common data types such as numbers, booleans, strings, bytes, arrays, sets, and maps. Many properties of these types can be expressed using universal quantifiers, requiring loops for verification in smart contracts, but can often be disproven by a counterexample or proven with a proof. Below are key properties for each type:

@@

To overcome these challenges, we propose a proof-of-work-based incentivization mechanism. We utilize the proof-of-work concept by introducing a target hash \( t \), which sets the required difficulty level to earn the computation reward. The basic idea is that each verification process introduces a target hash. The validator attempts to perform the negation check and compute a hash that is less than or equal to the given target hash. The objective of the validator is to find either a counterexample or a computation that produces a hash smaller than or equal to the target hash \( t \).
\subsubsection{Introduce a seed} To recheck the counterexample or computation proof on-chain at a reasonable gas cost, the counterexample or computation proof should be submitted on-chain in the form of the indication of the element \( a \in A \) where the assertion is invalid, in the case of a counterexample. The on-chain re-verification process is then straightforward, simply requiring the evaluation of \( \neg P(a) \).

@@

The seed \( s \) is a random number. 
\begin{gather*}
s \in \mathbb{N} 
\end{gather*}
The seed $s$  is then reduced with modulo \( n \) to obtain \( i \), which is associated with an element \( a \) in \( A \).
\begin{gather}
\label{eq:11}
i = (s\mod n) + 1
\end{gather}
\subsubsection{Estimate the number of seeds:} To ensure that a sufficient number of checkpoints have been checked before a computational proof is found, we first estimate the number of seeds required to find a counterexample with the desired probability of correctness.

@@

So the number of the seeds to achive the expected propety $p$ is great or at least equal to $m$. Note that, \( p \) represents the probability when only one validator participates. As more validators are involved, the probability of discovering a counterexample increases.
\subsubsection{Set up the taget hash:}
The above number of seed $m$ can then be used to set up the target hash $t$. The target hash $t$ can be calculated based on a desired difficulty level. In proof-of-work systems, difficulty is typically adjusted to ensure that the average efforts to find a valid hash. The target hash $t$ is often calculated by taking the maximum possible hash value and dividing it by the difficulty level.

@@

The inclusion of validators' addresses and \( r \) is crucial in preventing reward manipulation, as it ensures that a validator cannot resubmit with the same \( r \), thereby preventing repeated claims for the same computation proof or counterexample.
\section{Gas Cost Analysis}
\label{sec:gas-cost-analysis}
This section evaluates the cost of the proposed distributed verification method and compares it to traditional on-chain verification.
\subsection{Transaction Execution Costs}
Transaction costs, measured in gas, can be divided into five key components:
\begin{enumerate}
\item Base cost: Fixed cost for initiating a transaction, covering operations like hashing, signature verification, and balance updates. For instance, transferring ETH in Ethereum costs 21,000 gas.
\item Data cost: Gas tied to the size of the transaction’s data payload, with non-zero bytes incurring higher costs than zero bytes.
\item Computational cost: Gas for executing smart contract operations, such as arithmetic, logic, control flow, cryptography, and memory tasks.
\item Storage cost: Higher than computation, as it involves writing to persistent storage. %In Ethereum, writing a new value costs 20,000 gas, updates cost 5,000 gas, and reading costs 100 gas.
\item Refund gas: Gas refunded for specific operations, like using SELFDESTRUCT or resetting storage values to zero.
\end{enumerate}
Thus, the total gas cost (execution cost) includes base, data, computational, and storage costs.
\subsection{Comparative Analysis of On-Chain and Offline Distributed Methods}
We compare the gas costs of on-chain and off-chain verification by breaking down their components.
\subsubsection{On-chain Verification Gas Costs}
Let \( G_{parameter} \) represent the intrinsic gas cost, which includes base and data costs, primarily depending on the size of the parameter \( p \). The total on-chain gas cost \( G_{on} \), given in Equation \ref{on-gas}, includes:
\begin{itemize}
    \item Intrinsic gas \( G_{parameter} \),
    \item Optional storage gas \( G_{storage} \),
    \item Gas for \( n \) parameter checks, each costing \( G_{check} \),
    \item Execution gas \( G_{run} \), if the parameter is valid.
\end{itemize}
\begin{equation}
\label{on-gas}
G_{on} = G_{parameter} + [G_{storage}] + n \cdot G_{check} + G_{run}
\end{equation}

@@

\section{Related work}
\label{sec:related-work}
\section{Conclusion}
\label{sec:conclusion}
This paper proposes a method for parameter verification in smart contracts on the blockchain. The method addresses the challenge of performing computationally expensive verification processes directly on-chain. The core idea is to offload the verification process to an off-chain system, with only the verification results being submitted on-chain. To implement this approach, we propose an incentive mechanism that encourages validators to participate in the verification process while ensuring the correctness of the parameters when deemed valid. Our gas cost analysis demonstrates the benefits of this approach, particularly when dealing with large parameters that are costly to verify on-chain.
\newpage
\bibliographystyle{splncs04}
\bibliography{bio}
\end{document}

>>>>

\lstdefinelanguage{solidity}{
  backgroundcolor=\color{pink!20},
  keywords={contract, function, public, int},
  keywordstyle=\bfseries\color{blue},
  commentstyle=\itshape\color{green!40!black},
  basicstyle=\ttfamily,
  morecomment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]",
  sensitive=true
}
\begin{document}
%
\title{Gas-Efficient Parameter Verification for Blockchain Smart Contracts Using Off-Chain Validators}
%
\titlerunning{Off-Chain Parameter Verification Approach: Gas-Efficient}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Thi Thu Ha Doan\orcidID{0000-0001-7524-4497}\and Peter Thiemann\orcidID{0000-0002-9000-1239}}
%
\authorrunning{Ha Doan, P. Thiemann}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Freiburg, Germany \\
  \email{\{doanha,thiemann\}@informatik.uni-freiburg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
In certain blockchain scenarios, verifying the properties of parameters may require significant gas costs or be infeasible due to gas limits. This study proposes a distributed verification protocol to address these challenges. The core concept involves offloading the verification process to validators, who attempt to find counterexamples or proofs off-chain. If a counterexample is discovered, it can be submitted for re-verification on-chain. If validated, the parameter is discarded; otherwise, the correctness of the parameter is guaranteed through a proof-of-work incentive mechanism, encouraging validators to participate in the distributed verification process. To implement these ideas, we propose a practical model that also tackles potential security concerns. We developed a prototype of the protocol and conducted a cost analysis, demonstrating its gas efficiency and practical utility.
\keywords{blockchain, off-chain verification, gas optimization, proof-of-work, distributed verification}
\end{abstract}
%
%
%
\section{Introduction}
\label{sec:introduction}
\lstset{language=solidity}
A smart contract \cite{szabo1997smartcontracts,eth-whitepaper,tezos-whitepaper} is a critical component of blockchain technology, with applications ranging from simple tasks like auctions to more complex systems such as decentralized markets. However, broader adoption of smart contracts faces challenges, with gas costs being among the most significant. Every computation performed by a smart contract on the blockchain incurs a cost, as each unit of computation and storage consumed by an algorithm must be paid for due to the burden it places on the system \cite{eth-whitepaper,eth-yellowpaper,gas-cost}.

@@

Another scenario involves interactions with external data sources. Since smart contracts cannot directly access off-chain data, blockchain oracles \cite{blockchain-oracles,oracle-patterns,astraea,chainlink-whitepaper} supply this information. When external data becomes available, an oracle invokes a smart contract with the relevant information.

@@

Smart contract languages like Solidity \cite{solidity}, Vyper \cite{vyper}, Michelson \cite{michelson,michelson1}, and Plutus \cite{plutus} support common data types such as numbers, booleans, strings, bytes, arrays, sets, and maps. Many properties of these types can be expressed using universal quantifiers, requiring loops for verification in smart contracts, but can often be disproven by a counterexample or proven with a proof. Below are key properties for each type:

@@

To overcome these challenges, we propose a proof-of-work-based incentivization mechanism. We utilize the proof-of-work concept \cite{dwork1992pow,nakamoto2008bitcoin} by introducing a target hash \( t \), which sets the required difficulty level to earn the computation reward. The basic idea is that each verification process introduces a target hash. The validator attempts to perform the negation check and compute a hash that is less than or equal to the given target hash. The objective of the validator is to find either a counterexample or a computation that produces a hash smaller than or equal to the target hash \( t \).
\subsubsection{Introduce a seed} To recheck the counterexample or computation proof on-chain at a reasonable gas cost, the counterexample or computation proof should be submitted on-chain in the form of the indication of the element \( a \in A \) where the assertion is invalid, in the case of a counterexample. The on-chain re-verification process is then straightforward, simply requiring the evaluation of \( \neg P(a) \).

@@

The seed \( s \) is a random number. 
\begin{gather*}
s \in \mathbb{N} 
\end{gather*}
The seed $s$  is then reduced with modulo \( n \) to obtain \( i \), which is associated with an element \( a \) in \( A \).
\begin{gather}
\label{eq:11}
i = (s\mod n) + 1
\end{gather}
\subsubsection{Estimate the number of seeds:} To ensure that a sufficient number of checkpoints have been checked before a computational proof is found, we first estimate the number of seeds required to find a counterexample with the desired probability of correctness \cite{ross2014probability,feller1968probability}.

@@

So the number of the seeds to achive the expected propety $p$ is great or at least equal to $m$. Note that, \( p \) represents the probability when only one validator participates. As more validators are involved, the probability of discovering a counterexample increases.
\subsubsection{Set up the taget hash:}
The above number of seed $m$ can then be used to set up the target hash \cite{nakamoto2008bitcoin,bonneau2015sok}. The target hash $t$ can be calculated based on a desired difficulty level. In proof-of-work systems, difficulty is typically adjusted to ensure that the average efforts to find a valid hash. The target hash $t$ is often calculated by taking the maximum possible hash value and dividing it by the difficulty level.

@@

The inclusion of validators' addresses and \( r \) is crucial in preventing reward manipulation, as it ensures that a validator cannot resubmit with the same \( r \), thereby preventing repeated claims for the same computation proof or counterexample.
\section{Gas Cost Analysis}
\label{sec:gas-cost-analysis}
This section evaluates the cost of the proposed distributed verification method and compares it to traditional on-chain verification.
\subsection{Transaction Execution Costs}
Transaction costs \cite{eth-yellowpaper,chen2019underoptimized,victor2019measuring}, measured in gas, can be divided into five key components:
\begin{enumerate}
\item Base cost: Fixed cost for initiating a transaction, covering operations like hashing, signature verification, and balance updates. For instance, transferring ETH in Ethereum costs 21,000 gas.
\item Data cost: Gas tied to the size of the transaction’s data payload, with non-zero bytes incurring higher costs than zero bytes.
\item Computational cost: Gas for executing smart contract operations, such as arithmetic, logic, control flow, cryptography, and memory tasks.
\item Storage cost: Higher than computation, as it involves writing to persistent storage. %In Ethereum, writing a new value costs 20,000 gas, updates cost 5,000 gas, and reading costs 100 gas.
\item Refund gas: Gas refunded for specific operations, like using SELFDESTRUCT or resetting storage values to zero.
\end{enumerate}
Thus, the total gas cost (execution cost) includes base, data, computational, and storage costs.
\subsection{Comparative Analysis of On-Chain and Offline Distributed Methods}
We compare the gas costs of on-chain and off-chain verification by breaking down their components.
\subsubsection{On-chain Verification Gas Costs}
Let \( G_{parameter} \) represent the intrinsic gas cost, which includes base and data costs, primarily depending on the size of the parameter \( p \). The total on-chain gas cost \( G_{on} \), given in Equation \ref{on-gas}, includes:
\begin{itemize}
    \item Intrinsic gas \( G_{parameter} \),
    \item Optional storage gas \( G_{storage} \),
    \item Gas for \( n \) parameter checks, each costing \( G_{check} \),
    \item Execution gas \( G_{run} \), if the parameter is valid.
\end{itemize}
\begin{equation}
\label{on-gas}
G_{on} = G_{parameter} + [G_{storage}] + n \cdot G_{check} + G_{run}
\end{equation}

@@

\section{Related work}
\label{sec:related-work}
Smart contracts have been widely adopted to automate and secure decentralized applications. However, intensive on-chain computation can lead to high gas costs or exceed gas limits. To address this, many approaches focus on moving computations off-chain and distributing the verification process.

Layer 2 solutions like Plasma \cite{plasma-whitepaper} move heavy computation to a separate child chain anchored to the Ethereum Mainnet, improving scalability but not suited for parameter verification. More recently, optimistic rollups \cite{optimisticrollups} and zk-rollups \cite{zkrollups} emerged, offloading computation while preserving security. Optimistic rollups allow challenges through fraud proofs, similar to our counterexample mechanism, while zk-rollups use cryptographic proofs. However, both focus on transaction throughput, not complex parameter verification.

Decentralized oracle networks like Chainlink \cite{chainlink} enable off-chain data validation but are designed for fetching external data, not parameter verification. Their incentive model also differs from our proof-of-work mechanism.

zk-SNARKs and zk-STARKs \cite{groth2016snarks} allow efficient on-chain verification but are computationally demanding, making them impractical for continuous validation. Privacy-focused solutions like Hawk \cite{7546538} leverage hybrid on-chain/off-chain computation, aligning with our approach. Arbitrum \cite{10.5555/3277203.3277305} also supports off-chain computation, but primarily at the consensus level.

Our work builds on these foundations by proposing a distributed, incentive-driven off-chain verification model to improve gas efficiency and enable counterexample searches. Unlike prior approaches, our method focuses on parameter verification using a distributed network of validators. The proof-of-work mechanism incentivizes validators, ensuring correctness without the high costs of on-chain verification.
\section{Conclusion}
\label{sec:conclusion}
This paper proposes a method for parameter verification in smart contracts on the blockchain. The method addresses the challenge of performing computationally expensive verification processes directly on-chain. The core idea is to offload the verification process to an off-chain system, with only the verification results being submitted on-chain. To implement this approach, we propose an incentive mechanism that encourages validators to participate in the verification process while ensuring the correctness of the parameters when deemed valid. Our gas cost analysis demonstrates the benefits of this approach, particularly when dealing with large parameters that are costly to verify on-chain.
\newpage
\bibliographystyle{splncs04}
\bibliography{bio}
\end{document}
